ShrinkNets

### 2018-01-04 paper/paper.tex
pass by sam

\documentclass[sigconf]{acmart}
\sloppy
\usepackage{graphicx}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\makeatletter
\renewcommand\@formatdoi[1]{\ignorespaces}
\makeatother
\settopmatter{printacmref=false}

@@

\begin{document}
\title{ShrinkNets}

@@

When designing Neural Netowrks, finding the apropriate size (width and depth) is key. Indeed, these hyper parameters have a strong correlation with over/underfitting. The main problem is that we have no reliable way to find them [ref]. Decades of experimentation led to some heuristics [ref] that try to prune that immense space of possible network sizes, but we are still bound to use costly and sometimes complex methods to find reasonable values for these hyper-parameters.

@@

\par In the litterature we can see different ways of approaching this issue. The first one is to select parameters, train the model, evaluate it, repeat and pick the best one. There are many different ways of selecting parameters: random search [ref], grid search [ref], meta gradient descent [ref], parsen trees[ref], gaussian processes [ref] etc... but they all suffer from one major drawback: we have to train and evaluate countless models; and even if some algorithms allow parallel evaluations [ref] to reduce the overall training time, the hardware and energy cost is still important.
\par To reduce the number of models trained, another approach emerged: train a slightly bigger model and after convergence, remove as many parameters as possible without impacting the performance of the model. Notable contributions are Optimal Brain Dammage [ref], Deep Compression [ref], and Group sparsity [ref] (this one is especially related to this article). These techniques are very interesting but they still require a reasonable network size to start with, so they usually have to be combined with classic hyper-optimization techniques.
\par However, some recent contributions like Non-Parametric Neural Netowrks [ref] and [ref] try to learn the network size (width for the former and depth for the latter) during the training process and without any prior assumption about the network size.

@@

The method described in [ref] grows and shrink the network over time. Though it seems to be an attractive property to have, during our experiments and according to their results, models are very slow to train and sometimes converge to suboptimal solutions. Their method also required a new optimizer \textit{AdaRad}. Our goal was to provide a solution that can easily be integrated in existing machine learning systems and provide similar convergence speed and accuracy. Therefore, designing a new layer that only allow shrinking seemed to be best approach.

\subsection{Definition}

In this section we define the \textit{Filter Layer}. It takes an input of size $\left(B \times C \times D_1 \times \dots \times D_n\right)$. So it is compatible with fully connected layers with $n=0$ or convolutional layers with $n=2$. This layer has a parameter $\theta \in \mathbb{R}^C$ and is defined the following way.
\begin{equation}
  Filter(I;\theta) = I \circ \max(0, \theta)
\end{equation}

Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$ is expanded in all dimensions except the second one to match the input size. It is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be $0$. We can use this property to devise a training procedure.
\subsection{The training procedure}

To train networks we need start with a clearly oversized network, then we insert \textit{Filter Layers} in the architecture (usually after every Linear or Convolutional layer except the last one) and we sample their weight from the $\text{Uniform}(0, 1)$ distribution. We could train this network as it is and it would be equivalent to a normal neural netork. However, our goal is to find the smallest network with reasonable performance. We can achieve that by introducing sparsity in the parameters of the \textit{Filter Layers}. Indeed, having a negative value is equivalent to zeroing an entire row and column in the surrounding layers. These disabled neurons/channels can be removed from the network without changing its output. To obtain this sparsity we simply redefine the loss function:

@@

The $\lambda$ parameter controls the tradeof between optimizing the original loss or the size of the network.

@@

To obtain good performance using this approach, it is key to remove neurons and channels from the network as soon as possible. This task usually is cubbersome using existing machine learning frameworks. To enable the reproducibility of our results and let people use this method on their own dataset and architectures, we implemented a small library on top of \textit{PyTorch}. It makes it very easy to design and train networks that contains \textit{Filter Layers}. We will briefly describe the software architecture.
\par The key operation we want to perform is warn layers when a feature is removed so they can resize themselves. Therefore, we need to know what are the child and parents of a given layers. Since there is no concept of computation graph in \textit{PyTorch} we had to build it. Layers are augmented with a list of incoming modules (parents) and outgoing modules (children).
\par Edges in the graph carry features from parent to children. When a \textit{Filter Layer} removes a feature, edges need to be able to warn layers so we implemented them as an event hubs that maintain the list of features to keep; we called them \texttt{FeatureBags}. In many cases, layers do not change the number of features (eg. \textit{Dropout}, \textit{BatchNorm}), therefore, events needs to propagate through them to warn all layers that share the same number of features. To solve this problem, such layers instantiate \texttt{MirrorFeatureBags} which role is to relay events to and from the root \texttt{FeatureBag}. With this event-base approach are able to keep all the layers in sync. Adding layers becomes straightforward: programmers just have to react to three events: input removal, output removal and garbage collection. During our tests we ran the garbage collection every epoch.

@@

To demonstrate that the approach is viable, we will first show that Shrinking Networks converge. For this experiment we trained a one hidden layer neural network with one filter layer to control the number of hidden units. We initialized the models with $10000$ neurons and trained them on \texttt{MNIST} using different regularization factors ($\lambda$). We summarized the results on \autoref{convergence_plot}. [Should we explain the results ?]

@@

To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider two different architecture, a three hidden layer feed forward network and a \textit{LeNet-5} [ref]. We assume we do not know the number of channels and neurons and we want to find the best architecture by performing random search on the parameters that define the size. For classic neural networks these parameters are the number of channels and/or neurons; for ShrinkNets there is only one parameter $\lambda$. We sampled 50 models of each and trained them, picked the best epoch according to the validation accuracy and measured their performance on the testing set. Since ShrinkNets can be considered to be regularized in some sense, to make the comparison fair we also considered static networks with an $L2$ regularization factor (also drawn randomly). We summarized the accuracy we obtained on \autoref{hyper_opt_res}. [Should we explain the results]

@@

\par Even though the firsts results this techique yields seem promising, there are many area that we could explore to improve it. In the current implementation we only "learn" the number of features (neurons or channels). We could try to augment it with dynamic number of layers as seen in [ref] to be able to determine the entire architecture.
\par We saw on Figure \ref{convergence_plot} that the loss temporarly suffers from the removal of neurons. It is likely that the loss would be more stable if the number of neurons converged faster or neurons disapeared more progressively. This is why we think we should explore proximal gradient methods to optimize the filter vectors and/or randomize neuron removals.
\par During our evaluation we picked small datasets mainly to be able to train many models and have statistically significant distributions. With more computation resources and time, we could see if it generalises to bigger datasets and other architectures like \texttt{ResNet} [ref] (small modifications to the existing code base are required to support them)

>>>>

\documentclass[sigconf]{acmart}
\sloppy
\usepackage{graphicx}
\usepackage{color}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\makeatletter
\renewcommand\@formatdoi[1]{\ignorespaces}
\makeatother
\settopmatter{printacmref=false}

@@

\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\begin{document}
\title{ShrinkNets}

@@

When designing Neural Networks, finding the appropriate size (width and depth) is key. In particular, these hyper parameters have a strong correlation with over/underfitting \srm{give reference}. The main problem is that we have no reliable way to find them [ref]. Decades of experimentation led to some heuristics [ref] that try to prune that immense space of possible network sizes, but we are still bound to use costly and sometimes complex methods to find reasonable values for these hyper-parameters.

\srm{In this paper, we describe ... -- need to give a high level idea of solution, and its benefits.  Would be good to give your system/approach a name.}

@@

\par In the literature we can see different ways of approaching this issue. The first one is to select parameters, train the model, evaluate it, repeat and pick the best one. There are many different ways of selecting parameters: random search [ref], grid search [ref], meta gradient descent [ref], Parsen trees[ref], Gaussian processes [ref] etc... but they all suffer from one major drawback: we have to train and evaluate a very large number of models; and even if some algorithms allow parallel evaluations [ref] to reduce the overall training time, the hardware and energy cost is still very significant.
\par To reduce the number of models trained, another approach is to train a slightly bigger model and after convergence, remove as many parameters as possible without impacting the performance of the model. Notable contributions are Optimal Brain Damage [ref], Deep Compression [ref], and Group sparsity [ref] (this one is especially related to this article). These techniques are very interesting but they still require a reasonable network size to start with, so they usually have to be combined with classic hyper-optimization techniques.
\par However, some recent contributions like Non-Parametric Neural Netowrks [ref] and [ref] try to learn the network size (width for the former and depth for the latter) during the training process and without any prior assumption about the network size.
\srm{Give a short sentence about how our approach is different than these previous approaches.}

@@

\srm{This makes what we have done sound like an incremental change over prior work.  Instead, move this description to prior work and say why its not a good approach there, then describe what we do as a new method.  }
The method described in [ref] grows and shrinks the network over time. Though this seems to be an attractive property to have, during our experiments and according to their results, models are very slow to train and sometimes converge to suboptimal solutions. Their method also requires a new optimizer \textit{AdaRad}. Our goal was to provide a solution that can easily be integrated in existing machine learning systems and provide similar convergence speed and accuracy. Therefore, designing a new layer that only allow shrinking seemed to be best approach.
\srm{How is this shrinking approach different than previous approaches like Optimal Brain Damage, Deep Compression,e tc?}

\srm{Describe our key approach at a high level -- i.e., add a new layer to the network, called the {\it filter layer}, which ... }
\subsection{Definition}

In this section we define the \textit{Filter Layer}. It takes an input of size $\left(B \times C \times D_1 \times \dots \times D_n\right)$. So it is compatible with fully connected layers with $n=0$ or convolutional layers with $n=2$. This layer has a parameter $\theta \in \mathbb{R}^C$ and is defined the following way. \srm{Need to define B, C, D}.  
\begin{equation}
  Filter(I;\theta) = I \circ \max(0, \theta)
\end{equation}

Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$ is expanded in all dimensions except the second one to match the input size. It is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be $0$. We can use this property to devise a training procedure.  \srm{Give an English description of what this formalism achieves -- what does the filter layer do, why is it significant.}

\subsection{The training procedure}

To train networks we need start with a substantially oversized network, then we insert \textit{Filter Layers}  (usually after every linear or convolutional layer except the last one) and we sample their weight from the $\text{Uniform}(0, 1)$ distribution. We could train this network directly and it would be equivalent to a normal neural network. However, our goal is to find the smallest network with reasonable performance. We can achieve that by introducing sparsity in the parameters of the \textit{Filter Layers}. Indeed, \srm{having a negative value where?} having a negative value is equivalent to zeroing an entire row and column in the surrounding layers. These disabled neurons/channels can be removed from the network without changing its output (we describe how we perform this removal below). To obtain this sparsity we simply redefine the loss function:

@@

The $\lambda$ parameter controls the trade-off between optimizing the original loss or the size of the network.  \srm{Again give some intuitive description of what is novel / important about this choice of loss function and learning process.  It's hard to understand what is interesting/important about what you have done without you explicitly calling it out.}

@@

To obtain good performance using this approach, it is essential to be able to remove neurons and channels from the network as quickly as possible. This task usually is cumbersome using existing machine learning frameworks. To enable this, we implemented a small library on top of \textit{PyTorch} which makes it very easy to design and train networks that contains \textit{Filter Layers}. We will briefly describe the software architecture.
\par The key operation we want to perform is to notify layers when a feature is removed so they can resize themselves. Therefore, we need to track the child and parents each layer. Since there is no concept of computation graph in \textit{PyTorch} we had to build it;  specifically,  layers are augmented with a list of incoming modules (parents) and outgoing modules (children).
\par Edges in the graph carry features from parent to children. When a \textit{Filter Layer} removes a feature, edges need to notify layers of the change.  We implemented a simple event-based
architecture where edges send events about features to layers. 
\srm{Suggest cutting the following: Each  edge maintains a list of features to keep, and called a \texttt{FeatureBag}. In many cases, layers do not change the number of features (e.g., \textit{Dropout}, \textit{BatchNorm}), therefore, event needs to propagate through them to notify all layers that share the same number of features. To solve this problem, such layers instantiate \texttt{MirrorFeatureBags} which role is to relay events to and from the root \texttt{FeatureBag}.} With this event-based approach are able to keep all the layers in sync. Adding layers becomes straightforward: programmers just have to react to three events: input removal, output removal and garbage collection. \srm{What does garbage collection do?} During our tests we ran the garbage collection every epoch.

@@

To demonstrate that the approach is viable, we will first show that Shrinking Networks converge. For this experiment we trained a one hidden layer neural network with one filter layer to control the number of hidden units. We initialized the models with $10000$ neurons and trained them on \texttt{MNIST} using different regularization factors ($\lambda$). We summarized the results in \autoref{convergence_plot}. [Should we explain the results ?] \srm{Yes, you need to explain in detail -- what does this show?  How does it prove that your approach works / is a good idea?}

@@

To demonstrate the value of ShrinkNets in the context of hyper-parameter optimization we set up the following experiment: We consider two different architectures, a three hidden layer feed forward network and a \textit{LeNet-5} [ref]. We do not know the number of channels and neurons and we want to find the best architecture by performing random search on the parameters that define the size. For classic neural networks these parameters are the number of channels and/or neurons; for ShrinkNets there is only one parameter, $\lambda$. We sampled 50 models of each and trained them, picked the best epoch according to the validation accuracy and measured their performance on the testing set. Since ShrinkNets can be considered to be regularized in some sense, to make the comparison fair we also considered static networks with an $L2$ regularization factor (also drawn randomly) \srm{L2 regularization over what?}. We summarized the accuracy we obtained on \autoref{hyper_opt_res}. [Should we explain the results] \srm{Yes, need to describe in detail -- how does this prove that your method works/ is a good idea?  What are the key takeaways?}

@@

\par Even though the firsts results this technique yields seem promising, there are many area that we could explore to improve it. In the current implementation we only "learn" the number of features (neurons or channels). We could try to augment it with dynamic number of layers as seen in [ref] to be able to determine the entire architecture.
\par We saw on Figure \ref{convergence_plot} that the loss temporarily suffers from the removal of neurons. It is likely that the loss would be more stable if the number of neurons converged faster or neurons disappeared slower. For this reason we plan to explore proximal gradient methods to optimize the filter vectors and/or randomize neuron removals.
\par During our evaluation we picked small datasets mainly to be able to train many models and have statistically significant distributions. With more computation resources and time, we could see if it generalizes to bigger datasets and other architectures like \texttt{ResNet} [ref] (small modifications to the existing code base are required to support them)
